Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009]. Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks. After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency, that is, we estimated the percentile of the observed motif frequencies. Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone. To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network. In these models, we used the study identifiers in Table S1 as a random intercept. By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.

Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks. We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019]. To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the same group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class. Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies. To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network. We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept. By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level. To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].

>>>>

To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009]. Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks. After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies. Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone. To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network. In these models, we used the study identifiers in Table S1 as a random intercept. By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.

Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks. We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019]. To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class. Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies. To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network. We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept. By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level. To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
